Tolerant  to ethnic diversity, intolerant to intolerance

### 2020-01-26 ethnic_value_rum.Rmd
Broad lead research question

Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences

Lead Question (ex):
* how can we explain hybrid ethnic segregation patterns? (The Economist)
* hybrid segregation on value and ethnic for different types of people

@@

Define need of value similarity

Role of relative group size for both the ethnic and the value dimension

@@

Study 1: heterogeneity of ethnic preferences in agents \par
* Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$
* Same conditions, increase $\beta_v$

@@

>>>>

Diversity in cities: how to navigate the difference: Heterogeneity in ethnic preferences and competing preferences
People can rank their preferences differently based on their value-orientation
Still, ethnic groups can differ on their degree of ethnic, either value preferences

Literature on Schelling's model on heterogeneity within group (between agents) [@xie2012modeling]. Check for heterogeneity between groups

NEW: the competing homophily preference based on the value-orientation

Lead Question (ex): \par
* how can we explain hybrid ethnic segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? (The Economist) \par
* how can we explain hybrid value segregation patterns (some members of the same ethnic group are ethnically integrated, others are ethnically segregated)? \par
* what is the effect of value segregation on  ethnic segregation and vice versa? \par
* Factors underlying the mechanism of interest:  \par
- degree of parameter beta: how one dimension is important over the other in the relocation choice  \par
- relative group size for both the ethnic and the value dimension, since they would have a direct effect on the utility of a location
and on the number of agents defined as ethnicity-oriented and value-oriented
- heterogeneity within same ethnic group and between ethnic groups
* what is the role of heterogeneity in preferences within a group, and between groups? \par
* hybrid segregation on value and ethnic for different types of people \par
* What is the effect on such dynamics of relative group size \par

@@

We define the condition where people hold different ethnic and value preferences. We can impose at the individual level due by value-orientation that one group holds one preference higher than the other and that the degree of one preference is higher than the other one

DOUBT: if an agent likes "diversity", then I would expect the peak to change, and it being at $50 \%$ for the ethnic dimension, so integrationist attitudes, and the peak of value concentration of these agents to change according  to the $100 \%$ similar others integrationists, but you are making a different reasoning, that people aim at ethnic diversity, and the dimension of ethnicity would be less/more important in the relocation choice

The concept of heterogeneity is reflected into the experiments: \par
* individual: $\beta^\Box_e \geq \beta^\Box_v$, $\beta^\circ_v \geq \beta^\circ_e$  \par
* within ethnic group:  $\beta^\Box_e \geq \beta^\circ_e$, $\beta^\circ_v \geq \beta^\Box_v$, should specify the ethnic group  \par

This does not prevent than between groups there might be difference in terms of ethnic preferences, and similarly on value preferences

Define need of value similarity 
Role of relative group size for both the ethnic and the value dimension

@@

Study 1: heterogeneity of ethnic preferences in agents \par
* 1.1 Tune $\beta_e$ for all agents, with condition $\beta^\Box_e \geq \beta^\circ_e$, no difference between agents
* 1.2 Change  $\beta_e$ between groups (supported by literature on which group is going to be more conservative, or anyway argumented).
Observe the emergence of ethnic segregation first
* Same conditions, increase $\beta_v$ Either with first 1.1 and then compar, either compare first the effect of ethnic preference heterogeneity between groups over within group
In both cases, the effect of relative group sizes

@@

If a society is "conservative", the less ethnic-oriented of that society/scenario would have high level as well. In the end, you could narrow down so to have 3 conditions for each low, medium, high beta (e.g. 1, 5, 10), and calculate the $\beta_e$ of less ethnicity-oriented agents out of a ratio, e.g. min $n/n$,  $n/(n:2)$ (check), max $n/1$ \par
* 1 = 1,0.5,1 (check)
* 5 = 1,2.5,5
* 10 = 1,5,10
